Autonomous Aerial for Topological Mapping of Mars Environments

### 2018-06-09 Conference/SCITECH19/SCITECH19.tex
started numerical results txt

>>>>

In this section, we demonstrate the efficacy of the proposed 3D mapping and autonomous exploration with a simulated Mars environment. First we cover the software structure and parameters, then compare results using two different maps for entropy prediction.

\subsection{Software}

The mapping, exploration, and visualization processes communicate over the Robot Operating System (ROS) framework, and Gazebo 8 serves as the simulator for the physical objects and measurements.

\subsection{Results}
